A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator

### 2016-05-17 paper3_manuscript.tex
20160517

\begin{document}
\begin{frontmatter}
\title{Dual terminal sliding mode control}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

@@

@@

@@

(...background of sliding mode control...)\par
(...sliding mode control develop...)\par
Recent years, the sliding mode control has become a popular solution to the issue about various control and signal process missions \cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed \cite{meza2015output}. Zheng et al. implemented sliding mode control to eliminate the effect of the input quantization generated between the coder and the decoder \cite{zheng2016sliding}. Guzman et al. investigated the application of a sliding mode control in a power factor rectifier with constant switching frequency \cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method for a boost converter to guarantee the asymptotically stability \cite{oucheriah2013pwm}.  high order sliding mode control \cite{castillo2015higher,palosz2015laser}, super-twisting sliding mode\cite{zhao2015finite,liu2015second}
(...the terminal sliding mode develop...)\par
Normal linear hyperplane-based sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold. The first step is said to be the approaching phase which usually requires the states asymptotically or exponentially converge to the desired manifold, and the second step is the sliding phase which is related to the designed manifold closely. For achieving a fast convergence, the terminal sliding mode (TSM) control is developed based on the finite time control \cite{haimo1986finite,bhat1997finite,mu2016switching}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase. Owing to the fast convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in \cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal. \par
In this paper, a dual sliding mode (DSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties. A novel DSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly. A modified DSM (MDSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators. The remained paper is organized as follows: Section~\ref{sec:2} introduces a DSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified. In addition, we add performance parameters for improving the DSM scheme to obtain the MDSM scheme, and the newly presented method has a better performance in theoretical analysis. In Section~\ref{sec:3}, the MDSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out. Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
\section{Dual sliding mode control}\label{sec:2}

@@

where $bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system. For the system mentioned above, we can establish a desired dual sliding manifold as:

@@

There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the dual sliding mode control.

@@

As described in \cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:

@@

Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows \cite{moulay2006finite}:

@@

For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), dual sliding mode control inputs can be given according the following theorem.
\begin{mythm}\label{theorem:1}Dual Sliding Mode (DSM) Control Design.

@@

where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual sliding mode control inputs are formed in the following theorem.
\begin{mythm}\label{theorem:2}Modified Dual Sliding Mode (MDSM) Control Design.

@@

After introducing the parameters $\lambda$ and $\gamma$ into the DSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically. Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed. Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$. Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$. $\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it can be defined as the management parameter of the sliding status.

@@

The finite convergence of the DSM and MDSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs. Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition). For coping with the singularity, a nonsingular MDSM scheme is presented after introducing an analytical technique into the MDSM scheme based on the following lemma \cite{feng2013nonsingular}.

@@

Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme. Introducing the saturation terms into the original inputs yields:

@@

The proof is similar to the graphical analysis mentioned in \cite{feng2013nonsingular}, and omitted here.

@@

\section{Dual sliding mode control for rigid manipulators}\label{sec:3}
In this section, a dual sliding mode control is proposed for the rigid $2$-link robotic manipulator

@@

where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$. Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics \cite{feng2002non}:

@@

On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robotic manipulator by utilizing the following theorem.

@@

For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual sliding mode manifold is selected as

@@

&=\bm s^TM_0^{-1}(\bm q)(-\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2)+\bm\rho(t))\\

@@

At this point, the dual sliding mode control scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as

@@

Referring to Theorem \ref{theorem:4}, one can obtain the dual sliding mode control input for the even $n$-link manipulator. Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DSM scheme.

@@

The singularity of the DSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically. For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.

@@

In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DSM and MDSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.

@@

and one can produce a MDSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$. Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly. The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$. Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly. Therefore the design of the MDSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par

@@

At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
\begin{align}
\begin{split}
\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
\end{split}
\end{align}
where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}. Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates. One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control. More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison. Therefore these results show that the MDSM control scheme can achieve the regulation of the manipulator effectively.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{2}
\label{Figure:5}
\end{figure}
The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section. Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
\begin{align*}
&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
\end{align*}\par
The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDSM scheme. The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{2}
\label{Figure:6}
\end{figure}

>>>>

\begin{document}
\begin{frontmatter}
\title{A New Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator}
\author{Zhiqiang Ma}
\author{Guanghui Sun\corref{cor1}}
\ead{guanghuisun@hit.edu.cn}
\cortext[cor1]{Corresponding author}
\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}

@@

This paper proposes a novel dual terminal sliding mode control for rigid robotic manipulator. A new terminal sliding mode manifold design technique is addressed to achieve finite time convergence of the sliding phase, and furthermore utilizing the involved dual variables combines the individual sliding mode surfaces to obtain a integral sliding mode dynamics, the convergent time of which is also integral for the entire system. The newly proposed method also has the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motion of the rigid robotic manipulator. Simulation results validate the theoretical analysis about the proposed method. 

@@

Finite time control; Robotic manipulator control; Terminal sliding mode; Sliding mode manifold design; Stability analysis

@@

Variable structure systems (VSS) are best known due to its insensitivity to parameter variations and uncertainties~\cite{slotine1991applied}. Its widely utilization in practice case, such as DC and AC motors, process control, aircrafts, satellites, robots and so on, has validated robustness of VSS. As one of the most important branch of the VSS, the sliding mode control (SMC) has become a popular solution to the issue about various control and signal process missions in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second order sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC to eliminate the effect of the input quantization generated between the coder and the decoder~\cite{zheng2016sliding}. Guzman et al. investigated the application of a SMC in a power factor rectifier with constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to guarantee the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific mission, due to its insensitivity of parameters and uncertainties in system, however, there still exist some obstacles, such as noncontinuous switching input in high frequency and desired convergent speed design~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some practical engineering cases~\cite{fridman2011sliding}. \par
For alleviating the side effects, many researchers addressed remarkable approaches to improve the performance of the SMC scheme in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}. Among these methods, the high order sliding mode control and super-twisting sliding mode control efforts to generate the continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}, which eliminate the chattering by hiding the switching in high-order terms or absorbing the switching via some techniques. \par
Besides the issue on repressing the chattering, the fast convergence of the SMC scheme is also a hot subject. Normal linear sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold, and an accelerating operation usually occurs in this two phases. The first step is said to be the approaching phase which usually requires the states converge to the desired manifold in finite time, and selecting suitable Lyapunov function and control parameters may accelerate this process; the second step is the sliding phase which is related to the designed manifold closely, and normal manifold design techniques can just guarantee the asymptotically convergence. For achieving a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase to complete the global finite time convergence. Owing to the global finite time convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal. Feng et al. presented a global terminal sliding mode algorithm for manipulating the rigid robot, and produced the control design by using Lagrangian dynamic expression~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of terminal and super-twisting sliding-mode, providing a convergence control in finite time. \par
According to the achievements mentioned above, one can find that the conventional terminal sliding mode manifold design techniques are similar, since they are all based on the single variable finite time control, in another words, the sliding mode dynamics only involves the individual variable and its derivative essentially~\cite{mu2016switching}. This nature makes the TSM scheme become an individual control subsystem, which leads to the complicity of global convergent time in some extent. In this paper, an integral sliding mode manifold technique is proposed for finite time stability of the two-order system, and the novel manifold involves two variables to guarantee the integral finite time convergence, and the convergent time can be obtained easily. Also, the nonsingularity and chattering suppression are available in the scheme. \par
In this paper, a dual sliding mode (DTSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties. A novel DTSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly. A modified DTSM (MDTSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators. The remained paper is organized as follows: Section~\ref{sec:2} introduces a DTSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified. In addition, we add performance parameters for improving the DTSM scheme to obtain the MDTSM scheme, and the newly presented method has a better performance in theoretical analysis. In Section~\ref{sec:3}, the MDTSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out. Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
\section{Dual terminal sliding mode control}\label{sec:2}

@@

where $\bm x = [x_1,x_2,x_3,x_4]^T$ is the system vector state; $f(\bm x,t)$ and $b(\bm x,t)\neq 0$ are smooth nonlinear functions with respect to $\bm x$; $u_i(t)$, $i=1,2$ stands for the scalar input; $g_i(\bm x,t)$, $i=1,2$  is a defined as a bounded nonlinear function which satisfies $\Vert g_i(\bm x,t)\Vert\le l_i$, $l_i>0$, meaning the uncertainty and disturbance of the system. For the system mentioned above, we can establish a desired dual terminal sliding manifold as:

@@

There exist two lemmas about the finite convergence theory, providing convergent forms which contribute to the verification of the finite convergence about the DTSM control.

@@

As described in~\cite{moulay2006finite}, it is assumed that the continuous function $V(t)$ is positive-define, satisfying the following condition:

@@

Selecting $V(t) = \frac{x_1^2+x_2^2}{2}$ obtains the finite convergent time as follows~\cite{moulay2006finite}:

@@

For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), DTSM control inputs can be given according the following theorem.
\begin{mythm}\label{theorem:1}Dual Terminal Sliding Mode (DTSM) Control Design.

@@

where $\gamma$ is a positive constant and $\lambda\in R$ is a regulable parameter. Hence, the modified dual terminal sliding mode control inputs are formed in the following theorem.
\begin{mythm}\label{theorem:2}Modified Dual Terminal Sliding Mode Control Design.

@@

After introducing the parameters $\lambda$ and $\gamma$ into the DTSM scheme, the performances of the approaching and sliding phases become regulatable, meaning that these parameters can adjust the convergent time analytically. Although $\lambda$ does not appear in Eq.~(\ref{eq:total convergent time}), the establishment of $V(t_0)$ involves it when the state $\bm x(t_0)$ has been fixed. Strictly speaking, it affects the approaching distance between $V(t_0)$ and $V(t_r)$, and normally $V(t_r)$ stands for the reaching status at $t_r$, namely, $V(t)=\bm s^T(t)\bm s(t) = 0,\forall t\ge t_r$. Admittedly, the variety of $\lambda$ is only modestly helpful in this approaching time regulation due to its limited effect on $V(t_0)$. $\eta$ is said to be an ''approaching speed'' according to its function, a suitable selection of which will adjust the approaching time as desired in some extent. Hence, $\lambda$ cooperates with $\eta$ to manage the approaching status, and by utilizing the similar analysis, owing to $\gamma$ adjusting the speed of sliding phase, it can be defined as the management parameter of the sliding status.

@@

The finite convergence of the DTSM and MDTSM scheme has been verified clearly, but similar to the conventional terminal sliding mode control, there exists another obstacle in the design mentioned above, namely, the issue of the singularity in control inputs. Essentially, the singularity occurs in Eq.~(\ref{eq:modified input}) when $x_1=0$ but $x_2\neq 0$ in $u_1$ (the phenomena happens to $u_2$ under the same condition). For coping with the singularity, a nonsingular MDTSM scheme is presented after introducing an analytical technique into the MDTSM scheme based on the following lemma~\cite{feng2013nonsingular}.

@@

Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDTSM scheme, select a new inputs to complete the nonsingular MDTSM scheme. Introducing the saturation terms into the original inputs yields:

@@

The proof is similar to the graphical analysis mentioned in~\cite{feng2013nonsingular}, and omitted here.

@@

\section{Dual terminal sliding mode control for rigid manipulators}\label{sec:3}
In this section, a DTSM control is proposed for the rigid $2$-link robotic manipulator

@@

where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$. Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics~\cite{feng2002non}:

@@

On the basis of the above results, one can design the DTSM scheme for $2$-link robotic manipulator by utilizing the following theorem.

@@

For the rigid $2$-link manipulator~(\ref{eq:lagrangian system}), if the dual terminal sliding mode manifold is selected as

@@

&=\bm s^TM_0^{-1}(\bm q)(-k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}+\bm\rho(t))\\

@@

At this point, the DTSM scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as

@@

Referring to Theorem \ref{theorem:4}, one can obtain the DTSM input for the even $n$-link manipulator. Essentially, this technique requires that the sliding mode manifold has to consist of $n/2$ pairs of individual sliding surfaces, in another words, this design for the manifold can be regarded as a work for yielding manifolds of the $n/2$ sub-systems.\par
Considering the situation that $n$ is an odd number, the $n$-link manipulator as we know is assumed as a full-actuated system, and hence an individual dimension can be excluded by using conventional terminal sliding mode control, which results in that the remained $n-1$-link manipulator can be controlled by the proposed DTSM scheme.

@@

The singularity of the DTSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the DTSM control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically. For handling the chattering, the $sign()$ can be replaced with $sat(x,\delta)$, and the bounded value $\delta$ is determined according to actual needs.

@@

In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DTSM and MDTSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.

@@

and one can produce a MDTSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$. Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly. The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$. Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly. Therefore the design of the MDTSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par

@@

At this point, some effectiveness of the MDTSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDTSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
\begin{align}
\begin{split}
\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
\end{split}
\end{align}
where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}. Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDTSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates. One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDTSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control. More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDTSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison. Therefore these results show that the MDTSM control scheme can achieve the regulation of the manipulator effectively.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{2}
\label{Figure:5}
\end{figure}
The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section. Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
\begin{align*}
&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
\end{align*}\par
The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDTSM scheme. The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{2}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{2}
\label{Figure:7}
\end{figure}
\section{Conclusion}\label{sec:5}
A DTSM control for n-link robotic manipulator has been presented. The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design. The control scheme can guarantee the reaching condition of the desired sliding manifold, meanwhile the system states can converge to the origin along the desired manifold. Also, the entire convergent time can be calculated accordingly. Developing the basic DTSM yields the MDTSM control, providing a solution to eliminating chattering, avoiding singularity and fast convergence. For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}
